Twists of supersymmetric gauge theories

### 2019-08-19 paper.tex
Twisting arguments in dimensions 9 and 8

\subsubsection{Generalized BF theory}

@@

\subsubsection{Generalized Chern--Simons theory}

@@

@@

\chris{By the way, I see no obstruction to proving the following.  One just needs to check that the action of an infinitesimal symmetry $X$ in $\mf A'$ on the dimensionally reduced theory is by $\phi \mapsto i^*(X(p^*(\phi)))$, so that forming the reduced classical differential commutes with twisting.  This should follow from the definition of the supersymmetry algebra action on the reduced theory from the proposition above.}
\begin{lemma}
If $\mf A$ is an $n$-dimensional supersymmetry algebra, and $Q \in \mf A$ is a square-zero supercharge, then the operations of dimensional reduction from $\RR^n$ to $\RR^m$ and twisting by $Q$ commute.
\end{lemma}

@@

So, for the functionals at hand.  We'll use three properties of the action of $\so(n)$: that -- for spinovs $Q_1$ and  $Q_2$, and vectors $v$, we have that $X \cdot \Gamma(Q_1, Q_2) = \Gamma(X \cdot Q_1, Q_2) + \Gamma(Q_1, X \cdot Q_2)$,  $(X \cdot Q_1, Q_2) + (Q_1, X \cdot Q_2) = 0$, and that $X \cdot (\rho(v)Q) = \rho(X \cdot v)Q + \rho(v)(X \cdot Q)$.  These identities all follow from the equivariance of the pairing $\Gamma$, the scalar pairing $(,)$, and the Clifford multiplication $\rho$.  Using these facts, we compute
\begin{align*}
\{I_{\mr{rot}}, I^{(1)}\}(A,\lambda, A^\vee, \lambda^\vee, Q, X) &= \<X \cdot A^* , \Gamma(Q, \lambda)\> + \<A^* , \Gamma(Q, X \cdot \lambda)\> + \<X \cdot \lambda^*, \sd F_A Q\> +  \<\lambda^*, \sd F_{X \cdot A} Q\> \\
&= -\big(A^* , X \cdot \Gamma(Q, \lambda)\> - \<A^* , \Gamma(Q, X \cdot \lambda)\>\big) - \big(\<\lambda^*, X \cdot( \sd F_A Q)\> -  \<\lambda^*, \sd F_{X \cdot A} Q\>\big)\\
&= - \<A^* , \Gamma(X \cdot Q, \lambda)\> - \<\lambda^*, \sd F_A (X \cdot Q)\>\\
&= -\d^{\mr{rot}}_{\mr{CE}} I^{(1)}(A,\lambda, A^\vee, \lambda^\vee, Q, X),
\end{align*}
and
\begin{align*}
\{I_{\mr{rot}}, I^{(2)}\}(\lambda^\vee, Q_1, Q_2, X) &= \left\<X \cdot \lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> + \\
&\quad + \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) X \cdot \lambda^* + \frac 12 \left((Q_2, X \cdot \lambda^*)Q_1 + (Q_1, X \cdot \lambda^*)Q_2\right)\right\> \\
&= - \left\<\lambda^* \;,\; X \cdot(\rho(\Gamma(Q_1,Q_2)) \lambda^*) + \frac 12 \left((Q_2, \lambda^*)X \cdot Q_1 + (Q_1, \lambda^*)X \cdot Q_2\right)\right\> + \\
&\quad + \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) X \cdot \lambda^* - \frac 12 \left((X \cdot Q_2, \lambda^*)Q_1 - (X \cdot Q_1,  \lambda^*)Q_2\right)\right\> \\
&= - \left\<\lambda^* \;,\; \rho(\Gamma(X \cdot Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)X \cdot Q_1 + (X \cdot Q_1, \lambda^*)Q_2\right)\right\> - (1 \leftrightarrow 2)\\
&= -\d^{\mr{rot}}_{\mr{CE}} I^{(2)}(\lambda^\vee, Q_1, Q_2, X).
\end{align*}
\end{proof}

@@

\begin{theorem}
The minimal twist of 9d super Yang-Mills theory on the product of a Calabi-Yau 4-fold $X_4$ and an oriented 1-manifold $L = \RR$ or $S^1$ is equivalent to mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$.
\end{theorem}

The relevant fields for this calculation are those component fields which survived the 10d holomorphic twist of Theorem \ref{10d_twist_thm}.  These fields, in the BRST formalism, decompose as
\begin{align*}
B^{10} &= B + A \wedge \d \ol z^5 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR x_9) \\
A^{10}_{0,1} &= A' + \phi \d \ol z^5 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR x_9)
\end{align*}
along with the ghost $c$. \chris{can prove the theorem by the same argument as in 10d, or using dimensional reduction.}

@@

\subsubsection{The Holomorphic Twist}

@@

\subsubsection{The Rank 2 Twist}

% \cN=1 SYM, three twists

>>>>

\subsubsection{Generalized BF theory} \label{gen_BF_section}

@@

\subsubsection{Generalized Chern--Simons theory} \label{gen_CS_section}

@@

\chris{A question: are dimensional reductions, per this definition, unique?  I'd really like the answer to be yes (at least for dimensional reduction along a vector space), so that I can say the twist of a dimensional reduction is equivalent to \emph{the} (unique) dimensional reduction of the twist -- assuming the dimensional reductions before and after twisting exist (which, again, I'd like them to, at least for dimensional reduction along a vector space).}

@@

\chris{By the way, I see no obstruction to proving the following.  One just needs to check that the action of an infinitesimal symmetry $X$ in $\mf A'$ on the dimensionally reduced theory is by $\phi \mapsto i^*(X(p^*(\phi)))$, so that forming the reduced classical differential commutes with twisting.  This should follow from the definition of the supersymmetry algebra action on the reduced theory from the proposition above.}
\begin{lemma} \label{commuting_twist_and_reduction_lemma}
If $\mf A$ is an $n$-dimensional supersymmetry algebra, and $Q \in \mf A$ is a square-zero supercharge, then the operations of dimensional reduction from $\RR^n$ to $\RR^m$ and twisting by $Q$ commute.
\end{lemma}

We'll conclude this section by discussing some examples of dimensional reduction in the context of generalized BF and Chern-Simons theories.  First we'll describe what happens when we dimensionally reduce generalized Chern-Simons theory along $\RR$ in a holomorphic direction.

\begin{lemma} \label{CS_diml_red_lemma}
Let $\map(X \times C_{\ol \dd}, B\gg)$ be a generalized Chern-Simons theory as in Section \ref{gen_CS_section}, where $C = \CC$ or $\CC^\times$ is a curve, and $X = (X_1)_{\ol \dd} \times (X_2)_{\mr{Dol}} \times (X_3)_{\mr{dR}}$ is arbitrary.  Split $C$ as $L \times \RR$, where $L = \RR$ or $S^1$.  The \chris{assuming uniqueness} dimensional reduction of this theory along the map $X \times C \to X \times L$ is equivalent to the generalized Chern-Simons theory $\map(X \times L_{\mr{dR}}, B\gg)$.
\end{lemma}

\chris{I haven't made the notation here match the notation in Section \ref{gen_CS_section} yet.}

\begin{proof}
\chris{sketchy}
Let us denote the complex of BV fields in our generalized Chern-Simons theory on $X \times C$ by $(E_X \boxtimes \bigwedge^\bullet (T^{0,1}_C)^\vee) \otimes \gg[1]$, with differential on the sheaf of sections given by $Q_X + \ol \dd_C + \ell_1$ and pairing on the sheaf of sections by $\omega_X \boxtimes \omega_C$. Write $p$ for the projection $C \to L$.  It's enough to observe that there is a canonical graded isomorphism $p^*\Omega^\bullet(L) \iso \Omega^{0,\bullet}(C)$ intertwining on the one hand the de Rham and Dolbeault differentials, and on the other hand the two integration maps against the orientation on $L$ and the Calabi-Yau structure on $C$.
\end{proof}

What about if we, instead, reduce generalized Chern-Simons theory in a de Rham direction?

\begin{lemma} \label{CS_to_BF_diml_red_lemma}
Consider a generalized Chern-Simons theory of the form $\map(X \times \RR_{\mr{dR}}, B\gg)$, where again $X$ is arbitrary.  The dimensional reduction of this theory along the map $X \times \RR \to X$ is equivalent to the generalized BF type theory $\map(X, T[1]B\gg)$.
\end{lemma}

\begin{proof}
\chris{...}
\end{proof}

@@

So, for the functionals at hand.  We'll use three properties of the action of $\so(n)$: that -- for spinors $Q_1$ and  $Q_2$, and vectors $v$, we have that $X \cdot \Gamma(Q_1, Q_2) = \Gamma(X \cdot Q_1, Q_2) + \Gamma(Q_1, X \cdot Q_2)$,  $(X \cdot Q_1, Q_2) + (Q_1, X \cdot Q_2) = 0$, and that $X \cdot (\rho(v)Q) = \rho(X \cdot v)Q + \rho(v)(X \cdot Q)$.  These identities all follow from the equivariance of the pairing $\Gamma$, the scalar pairing $(,)$, and the Clifford multiplication $\rho$.  Using these facts, we compute
\begin{align*}
\{I_{\mr{rot}}, I^{(1)}\}(A,\lambda, A^\vee, \lambda^\vee, Q, X) &= \<X \cdot A^* , \Gamma(Q, \lambda)\> + \<A^* , \Gamma(Q, X \cdot \lambda)\> + \<X \cdot \lambda^*, \sd F_A Q\> +  \<\lambda^*, \sd F_{X \cdot A} Q\> \\
&= -\big(A^* , X \cdot \Gamma(Q, \lambda)\> - \<A^* , \Gamma(Q, X \cdot \lambda)\>\big) - \big(\<\lambda^*, X \cdot( \sd F_A Q)\> -  \<\lambda^*, \sd F_{X \cdot A} Q\>\big)\\
&= - \<A^* , \Gamma(X \cdot Q, \lambda)\> - \<\lambda^*, \sd F_A (X \cdot Q)\>\\
&= -\d^{\mr{rot}}_{\mr{CE}} I^{(1)}(A,\lambda, A^\vee, \lambda^\vee, Q, X),
\end{align*}
and
\begin{align*}
\{I_{\mr{rot}}, I^{(2)}\}(\lambda^\vee, Q_1, Q_2, X) &= \left\<X \cdot \lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\> + \\
&\quad + \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) X \cdot \lambda^* + \frac 12 \left((Q_2, X \cdot \lambda^*)Q_1 + (Q_1, X \cdot \lambda^*)Q_2\right)\right\> \\
&= - \left\<\lambda^* \;,\; X \cdot(\rho(\Gamma(Q_1,Q_2)) \lambda^*) + \frac 12 \left((Q_2, \lambda^*)X \cdot Q_1 + (Q_1, \lambda^*)X \cdot Q_2\right)\right\> + \\
&\quad + \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) X \cdot \lambda^* - \frac 12 \left((X \cdot Q_2, \lambda^*)Q_1 - (X \cdot Q_1,  \lambda^*)Q_2\right)\right\> \\
&= - \left\<\lambda^* \;,\; \rho(\Gamma(X \cdot Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)X \cdot Q_1 + (X \cdot Q_1, \lambda^*)Q_2\right)\right\> - (1 \leftrightarrow 2)\\
&= -\d^{\mr{rot}}_{\mr{CE}} I^{(2)}(\lambda^\vee, Q_1, Q_2, X).
\end{align*}
\end{proof}

@@

Let's describe the twist of 9-dimensional $\mc N=1$ theory with respect to such a supercharge.  The relevant fields for this calculation are those component fields which survived the 10d holomorphic twist of Theorem \ref{10d_twist_thm}.  These fields, in the BRST formalism, decompose, under the action of $\SU(4)$ into the following component fields:
\begin{align*}
B^{10} &= B + A \wedge \d \ol z^5 \in (\Omega^{0,2}(\CC^4; \gg) \oplus \Omega^{0,1}(\CC^4; \gg)) \otimes \Omega^0(\RR x_9) \\
A^{10}_{0,1} &= A' + \phi \d \ol z^5 \in (\Omega^{0,1}(\CC^4; \gg) \oplus \Omega^0(\CC^4; \gg)) \otimes \Omega^0(\RR x_9)
\end{align*}
along with the ghost $c$.  We'll describe the twisted action functional using dimensional reduction.

\begin{theorem} \label{9d_twist_thm}
The minimal twist of 9d super Yang-Mills theory on the product of a Calabi-Yau 4-fold $X_4$ and an oriented 1-manifold $L = \RR$ or $S^1$ is equivalent to mixed Chern-Simons theory on $X_4 \times L_\mr{dR}$.
\end{theorem}

\begin{proof}
Let's apply Lemma \ref{commuting_twist_and_reduction_lemma} -- the fact that twisting commutes with dimensional reduction.  Choose a representative element $Q$ in the equivalence class of square-zero supercharges which also squares to zero in the 10d $\mc N=(1,0)$ supersymmetry algebra.  According to Lemma \ref{commuting_twist_and_reduction_lemma}, the twist of 9d $\mc N=1$ super Yang-Mills theory by the supercharge $Q$ is equivalent to the dimensional reduction of holomorphic Chern-Simons theory on $X_4 \times C$, where $C = L \times \RR$ is either the curve $\CC$ if $L = \RR$, or $\CC^\times$ if $L = S^1$.

As such, it's sufficient to observe that mixed Chern-Simons theorem on $X_4 \times L_{\mr{dR}}$ is a dimensional reduction of holomorphic Chern-Simons theory on $X_4 \times C$, which follows by applying Lemma \ref{CS_diml_red_lemma}.
\end{proof}

\begin{remark}
One can, alternatively, prove this theorem using exactly the same methods as Theorem \ref{10d_twist_thm}; the steps that one needs to follow are identical.
\end{remark}

@@

\subsubsection{The Holomorphic Twist}
Square-zero supercharges in the 10d $\mc N=(1,0)$ supersymmetry algebra correspond to holomorphic supercharges in the 8d $\mc N=1$ supersymmetry algebra.  As such, we can calculate the holomorphic twist of 8d $\mc N=1$ super Yang-Mills by dimensionally reducing the holomorphic twist of 10d $\mc N=(1,0)$ super Yang-Mills along a copy of $\CC$.  This theory can, however, be made canonically $\ZZ$-graded.

\begin{theorem} \label{8d_holo_twist_thm}
The holomorphic twist of 8d $\mc N=1$ super Yang-Mills theory on a Calabi-Yau 4-fold $X_4$ is equivalent to holomorphic BF theory on $X_4$.
\end{theorem}

\begin{proof}
We can demonstrate this by applying Lemma \ref{CS_to_BF_diml_red_lemma} to the minimal twist of 9d super Yang-Mills theory, as calculated in Theorem \ref{9d_twist_thm}.  Indeed, \chris{...}
\end{proof}

\subsubsection{The Rank 2 Twist}
We'll next discuss the example of the twist by a rank 2 spinor, where both $\lambda_+$ and $\lambda_-$ are non-zero.  We can understand this twist by a second application of Lemma \ref{CS_diml_red_lemma} to the 9-dimensional $\mc N=1$ theory, or equivalently, by applying the lemma twice to the 10-dimensional $\mc N=(1,0)$ super Yang-Mills theory.  This twisted theory is only $\ZZ/2\ZZ$-graded, just like its higher-dimensional counterparts.

\begin{theorem} \label{8d_rank2_twist_thm}
The twist by a rank 2 supercharge of 8d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau 3-fold $X_3$ with a pair $L_1 \times L_2$ of oriented 1-manifolds is equivalent to mixed Chern-Simons theory on $X_3 \times (L_1 \times L_2)_{\mr{dR}}$.
\end{theorem}

\begin{proof}
The proof here is identical to the proof of Theorem \ref{9d_twist_thm}, we just start with the holomorphic twist of 10d super Yang-Mills theory on $X_3 \times C_1 \times C_2$, and apply Lemma \ref{CS_diml_red_lemma} twice.
\end{proof}

\chris{we need to comment on the fact that the rank 2 supercharge is stabilized by $\SU(3)$, but I'm not sure whether this is the entire stabilizer.}

@@

\chris{Here we're going to decompose the Yang-Mills fields under $\spin(7)$.  The vector of $\so(8)$ becomes the 8d Dirac spinor representation, and the two Weyl spinor representations both split as $7+1$, so the fields look like $\psi$, $A_+, A_-, \phi_+, \phi_-$.}
